Resource Adequacy and Operational Security Interaction in the EPOC 2030-50 Project

### 2022-05-23 papers/main.tex
Continue writing up results

\section{Input data - stylised Belgian grid with a large amount of renewables}

@@

\begin{table}
    \begin{tabular}{ccccc}
        \toprule
        UC  & DANet & PSCD & Load shedding [MWh] & Objective \\
            &       &      & 0.0                 & 101,916 \\
        \xm &       &      & 0.0                 & 212,558 \\
        \xm & \xm   &      & 0.0                 & 252,327 \\
        \xm & \xm   & \xm  & 0.0                 & 252,327 \\
    \end{tabular}
    \caption{Analysis of model results when operating reserves are not included. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simulataneous Charging and Discharging constraints.}
\end{table}

>>>>

\section{Input data - stylised Belgian grid with a large amount of variable renewable energy sources}

@@

\tabref{tab:results_no_OR} lists results for an increasing level of technical constraints or increasingly inflexible system. While the objective more than doubles going from the simple linear economic dispatch model with no network constraints to the unit commitment model with network constraints, no load shedding occurs. Preventing simultaneous charging and discharging constraints does not affect results at all, implying that additional energy consumption from storage does not aid congestion.

\begin{table}
    \begin{tabular}{ccccc}
        \toprule
        UC  & DANet & PSCD & Load shedding [MWh] & Objective \\
            &       &      & 0.0                 & 101,916   \\
        \xm &       &      & 0.0                 & 212,558   \\
        \xm & \xm   &      & 0.0                 & 252,327   \\
        \xm & \xm   & \xm  & 0.0                 & 252,327   \\
    \end{tabular}
    \caption{Analysis of model results when operating reserves are not included. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints.}\label{tab:results_no_OR}
\end{table}

\subsection{Probabilistic operating reserves with no reserve activation network constraints}

\begin{itemize}
    \item Unit commitment constraints lead to unavoidable load shedding. 
    \item Results should be interpreted with caution however, since reserve provision is quite strict (storage can't provide reserves, non spinning reserves not modelled).
    \item Network constraints are less problematic than unit commitment (cost increase of ~20,000 euros instead of 500,000) (perhaps thanks to storage, who knows).
    \item Preventing simultaneous charge and discharge has a small but noticeable effect.
\end{itemize}

\begin{table}
    \begin{tabular}{ccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
            &       &      & 0.0 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 0.5 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 1.0 & 0.0                 & 0.0                    & 117,290   \\
        \midrule
        \xm &       &      & 0.0 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 0.5 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 1.0 & 1,669               & 0.0                    & 645,679   \\
        \midrule
        \xm & \xm   &      & 0.0 & 1,669               & 0.0                    & 665,010   \\
        \xm & \xm   &      & 0.5 & 1,669               & 136                    & 657,010   \\
        \xm & \xm   &      & 1.0 & 1,669               & 136                    & 657,010   \\
        \midrule
        \xm & \xm   & \xm  & 0.0 & 1,669               & 0.0                    & 665,705   \\
        \xm & \xm   & \xm  & 0.5 & 1,669               & 136                    & 665,696   \\
        \xm & \xm   & \xm  & 1.0 & 1,669               & 136                    & 665,696   \\
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}

\subsection{Probabilistic operating reserves with reserve activation network constraints}

\begin{itemize}
    \item Unit commitment constraints lead to unavoidable load shedding. 
    \item Results should be interpreted with caution however, since reserve provision is quite strict (storage can't provide reserves, non spinning reserves not modelled).
    \item Network constraints are less problematic than unit commitment (cost increase of ~20,000 euros instead of 500,000) (perhaps thanks to storage, who knows).
    \item Preventing simultaneous charge and discharge has a small but noticeable effect.
\end{itemize}

\begin{table}
    \begin{tabular}{ccccccc}
        \toprule
        UC  & DANet & PSCD & RSL & Load shedding [MWh] & Reserve Shedding [MWh] & Objective \\
            &       &      & 0.0 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 0.5 & 0.0                 & 0.0                    & 117,290   \\
            &       &      & 1.0 & 0.0                 & 0.0                    & 117,290   \\
        \midrule
        \xm &       &      & 0.0 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 0.5 & 1,669               & 0.0                    & 645,679   \\
        \xm &       &      & 1.0 & 1,669               & 0.0                    & 645,679   \\
        \midrule
        \xm & \xm   &      & 0.0 & 1,669               & 0.0                    & 665,010   \\
        \xm & \xm   &      & 0.5 & 1,669               & 136                    & 657,010   \\
        \xm & \xm   &      & 1.0 & 1,669               & 136                    & 657,010   \\
        \midrule
        \xm & \xm   & \xm  & 0.0 & 1,669               & 0.0                    & 665,705   \\
        \xm & \xm   & \xm  & 0.5 & 1,669               & 136                    & 665,696   \\
        \xm & \xm   & \xm  & 1.0 & 1,669               & 136                    & 665,696   \\
    \end{tabular}
    \caption{Analysis of model results with operating reserves but no reserve activation network constraints. UC = Unit Commitment constraints, DANet = Day Ahead Network constraints, PSCD = Prevent Simultaneous Charging and Discharging constraints, RSL = Reserve Shedding Limit.}\label{tab:results_no_RANet}
\end{table}
